---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r setOptions,echo=FALSE}
# Don't switch to scientific notation until we're over 1e6
options(scipen=2)
```

## Loading and preprocessing the data
The data file is compressed in "activity.zip". Unzip the file and read the csv.
```{r loadData,echo=TRUE}
utils::unzip("activity.zip")
activityData <- read.csv("activity.csv")
colnames(activityData)
```

## What is mean total number of steps taken per day?
```{r stepsPerDay,echo=TRUE}
stepsPerDay <- aggregate(steps ~ date, data=activityData, sum)
head(stepsPerDay)
hist(stepsPerDay$steps,10,xlab = "Steps Per Day", main = "Histogram of Steps Per Day")
meanTotalStepsPerDay = round(mean(stepsPerDay$steps))
medianTotalStepsPerDay = median(stepsPerDay$steps)
```
The mean total steps per day is `r meanTotalStepsPerDay` and the median is `r medianTotalStepsPerDay`

## What is the average daily activity pattern?
```{r dailyPattern,echo=TRUE}
dailyPattern <- aggregate(steps ~ interval, data=activityData, mean)
plot(dailyPattern$interval, dailyPattern$steps, type="l", xlab="5min window during day", ylab="avg. steps", main="Daily activity pattern: Average steps per 5min interval")
maxSteps <- dailyPattern[match(max(dailyPattern$steps), dailyPattern$steps),]
abline(v=maxSteps$interval,col="red")
```

The interval with the highest average steps is `r maxSteps$interval` with `r round(maxSteps$steps,2)` steps.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
